\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-05-14 paper.qmd
Update hexbin algorithm with buffer: q
Update hexbin configurations with q

The value for $b_2$ is computed by fixing $b_1$. Considering the lower bound of the NLDR, $a_1 > 2 \times s_1$, and $a_1 > \frac{1-s_1}{b_1 -1}$. Similarly, according to the upper bound of the NLDR, $a_1 > \frac{2(r_2 - s_2)}{\sqrt{3}(b_2 - 1)}$, because $a_2 = \frac{\sqrt(3)}{2}a_1$ for regular hexagons. Therefore, $b_2 = \Big\lceil1 +\frac{2(r_2 - s_2)(b_1 - 1)}{\sqrt{3}(1-s_1)}\Big\rceil$.

@@

```{r}
#| label: fig-hex-param
#| fig-cap: "Hexagon binning parameters."
#| fig-width: 3
#| fig-height: 3
#| fig-pos: H

>>>>

The value for $b_2$ is computed by fixing $b_1$. Considering the lower bound of the NLDR, $a_1 > -2q$, and $a_1 > \frac{1+q}{b_1 -1}$. Similarly, according to the upper bound of the NLDR, $a_1 > \frac{2r_2(1 + q)}{\sqrt{3}(b_2 - 1)}$, because $a_2 = \frac{\sqrt(3)}{2}a_1$ for regular hexagons. Therefore, $b_2 = \Big\lceil1 +\frac{2r_2(b_1 - 1)}{\sqrt{3}}\Big\rceil$.

@@

```{r}
#| label: fig-hex-param
#| fig-cap: "Notations for hexagonal grid configurations."
#| fig-width: 3
#| fig-height: 3
#| fig-pos: H

### 2024-05-14 paper.tex
Update hexbin algorithm with buffer: q
Update hexbin configurations with q

The value for \(b_2\) is computed by fixing \(b_1\). Considering the
lower bound of the NLDR, \(a_1 > 2 \times s_1\), and
\(a_1 > \frac{1-s_1}{b_1 -1}\). Similarly, according to the upper bound
of the NLDR, \(a_1 > \frac{2(r_2 - s_2)}{\sqrt{3}(b_2 - 1)}\), because
\(a_2 = \frac{\sqrt(3)}{2}a_1\) for regular hexagons. Therefore,
\(b_2 = \Big\lceil1 +\frac{2(r_2 - s_2)(b_1 - 1)}{\sqrt{3}(1-s_1)}\Big\rceil\).

@@

\caption{\label{fig-hex-param}Hexagon binning parameters.}

>>>>

The value for \(b_2\) is computed by fixing \(b_1\). Considering the
lower bound of the NLDR, \(a_1 > -2q\), and
\(a_1 > \frac{1+q}{b_1 -1}\). Similarly, according to the upper bound of
the NLDR, \(a_1 > \frac{2r_2(1 + q)}{\sqrt{3}(b_2 - 1)}\), because
\(a_2 = \frac{\sqrt(3)}{2}a_1\) for regular hexagons. Therefore,
\(b_2 = \Big\lceil1 +\frac{2r_2(b_1 - 1)}{\sqrt{3}}\Big\rceil\).

@@

\caption{\label{fig-hex-param}Notations for hexagonal grid
configurations.}
